### 2022-11-02 ArticleAggregator_v05_pure.qmd
Initial upload

---
title: "Peripheral Edema measurement methods (by ArticleAggregator_v03)"
author: "ReCodeR"
format: html
server: shiny
editor: 
  markdown: 
    wrap: 72
---

## Sources of Articles

You should use:

-   Scopus
-   Web of Science
    -   [wosr](https://cran.r-project.org/web/packages/wosr/wosr.pdf)
-   Pubmed
-   EMBASE (for posters)
-   Scholar (including patents)

## Code
Use approach from [vignette](http://cran.nexr.com/web/packages/easyPubMed/vignettes/easyPM_vignette_html.html)

```{r}
#| label: Install packages
install.packages("rvest")
install.packages("dplyr")
install.packages("httr")
install.packages("writexl")
install.packages("easyPubMed")

```

```{r}
#| label: Load packages
library("rvest")
library("dplyr")
library("httr")
library("stringr")
library("glue")
library("writexl")
library("purrr")
library("readxl")
library("xml2")
library("easyPubMed")
```

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT",      "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "'peripheral edema' measurement"
aa_path <- r"(C:\Users\I0172484\Documents\01 - Projects\LevoAmlo 2022 Cecko\Edema Study Oct2022\Method Literature Review\)"
setwd(aa_path)
```

## EMBASE Manual export

```{r}
#| label: Load file exported from EMBASE with standard columns
eb_std_col <- read_xlsx(glue("{aa_path}Edema_Methods_eb_exp.xlsx"))
eb_std_col_names <- c("Title", "AuthorAll", "Year", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "FTlink", "EBlink", "OpenLink")
names(eb_std_col) <- eb_std_col_names

eb <- eb_std_col %>% 
  mutate(Author=str_extract(AuthorAll, pat="\\w+(?=\\s)")) %>% 
  select(-AuthorAll) %>% 
  mutate(Info=NA) %>% 
  mutate(Src="EMBASE") %>% 
  select(Title, Author, Year, FTlink, Src, Info, everything())

# write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
# Correct for Van Der Lee manually

```

## Google Scholar Using rvest

```{r}
#| label: Load Google Scholar page
gs_term <- str_replace_all(term, " ", "+")
my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=0%2C5&q={gs_term}")
gs <- read_html(my_uri)
n_hits <- gs %>% html_elements("#gs_ab_md .gs_ab_mdw") %>% html_text() %>% str_extract("\\d+") %>% as.integer()
n_pg <- n_hits %/% 10 + 1
# n_pg <- gs %>% html_elements("#gs_n a") %>% html_text() %>% as.integer() %>% na.omit() %>% max()

res_df <- tibble(
  title = character(),
  info = character(),
  ref = character()
)

for (i in 0:n_pg){
  curr_pg <- i*10
  print(curr_pg)
  my_uri_pg <- glue("https://scholar.google.com/scholar?start={curr_pg}&q={gs_term}&hl=en&as_sdt=0,5&as_vis=1")
  curr_pg <- read_html(my_uri_pg)
  art_title <- curr_pg %>% html_elements("h3 a") %>% html_text()
  art_info <- curr_pg %>% html_elements(".gs_a") %>% html_text()
  art_ref <- curr_pg %>% html_elements(".gs_rt") %>% html_elements("a") %>% html_attr("href")

  curr_df <- data.frame(title=art_title, info=art_info, ref=art_ref)
  res_df <- bind_rows(res_df, curr_df)
}

# art_title <- gs %>% html_elements("h3 a") %>% html_text()
# art_info <- gs %>% html_elements(".gs_a") %>% html_text()
# art_ref <- gs %>% html_elements(".gs_rt") %>% html_elements("a") %>% html_attr("href")
# output_df <- data.frame(title=art_title, info=art_info, ref=art_ref)
# write_xlsx(res_df, glue("{aa_path}gs_raw.xlsx"))
```

```{r}
#| label: Split content of column "info"
# res_df <- read_xlsx(glue("{aa_path}gs_raw.xlsx"))
sep_df <- res_df %>% 
  mutate(year=str_extract(info, pat="\\d+")) %>% 
  mutate(author=str_extract(info, pat="(?<=[A-Z]\\s([A-Z]\\s)?)\\w+(?=\\,\\s|\\s-)")) %>% 
  select(title, author, year, info, ref)

# rename colums to be compatible with EMBASE and fill missing columns
names(sep_df) <- c("Title", "Author", "Year", "Info", "FTlink")

```

```{r}
#| label: Expand Google Search (gs) columns to fit with EMBASE
gs <- sep_df %>% 
  mutate(PubDate = NA) %>% 
  mutate(PubType = NA) %>%
  mutate(Abstract = NA) %>% 
  mutate(CT = NA) %>%
  mutate(PMID = NA) %>% 
  mutate(PUI = NA) %>%
  mutate(DOI = NA) %>% 
  mutate(EBlink = NA) %>%
  mutate(OpenLink = NA) %>% 
  mutate(Src = "GoogleScholar") %>% 
  select(Title, Author, Year, FTlink, Src, Info, everything())

write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))
## Manually input missing values ;)
```
## Pubmed

You can get full-text link using Elink method of NIH e-utilities tool

```{r}
#| label: PubMed connection
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
pm_query <- glue('peripheral edema measurement')
my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
# my_abstracts_txt <- fetch_pubmed_data(my_entrez_id, format = "abstract")
# print(my_abstracts_txt[1:45])

my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id)
print(paste0("Query retireved ",my_entrez_id$Count," records."))
# print(my_abstracts_xml)
# write(my_abstracts_xml, file = "PubMed_records_by_write.xml")
# recs <- read_xml(my_abstracts_xml) #  From DB connection
recs <- read_xml(paste0(aa_path, "PubMed_records_by_write.xml")) # From file

# USE THIS  TO EXTRACT ALL FIELDS AND CHARACTER VECTOR AND JOIN TO DATAFRAME

xml_abstract_n <- recs %>% xml_find_all(".//Abstract") %>% length()
xml_pmid_n <- recs %>% xml_find_all(".//MedlineCitation/PMID | .//BookDocument/PMID") %>% length()
xml_year_n <- recs %>% xml_find_all(".//PubDate/Year | .//PubDate/MedlineDate") %>% length()
xml_author_n <- recs %>% xml_find_all(".//AuthorList") %>% xml_find_first(".//Author/LastName") %>% length()
xml_title_n <- recs %>% xml_find_all(".//ArticleTitle") %>% length()

# CONTINUE HERE ----
# Some articles have Either EIdType OR IdType OR BOTH.I need IF to remove those with both
xml_doi_n <- recs %>% xml_find_all(".//Article/ELocationID[@EIdType='doi']") %>% length() # N201
xml_doi_n <- recs %>% xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi'] | .//Article/ELocationID[@EIdType='doi']") %>% length() # N528
# WRONG if
# inspire here: https://stackoverflow.com/questions/30604107/r-conditional-evaluation-when-using-the-pipe-operator
xml_doi_n <- recs %>% {if(xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']") . else xml_find_all(".//Article/ELocationID[@EIdType='doi']")} %>% length()

art <- ".//PubmedArticle | .//PubmedBookArticle"
e_doi <- ".//Article/ELocationID[@EIdType='doi']"
p_doi <- ".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']"
n_art <- recs %>% xml_find_all(art)
xml_doi_n <- recs %>% xml_find_all(art) %>%
  map(if(is_empty(xml_find_first(p_doi)))
  xml_find_first(e_doi) else
  xml_find_first(p_doi)) %>% 
  length()

xml_doi_n <- recs %>% xml_find_all(art) %>%
  map(., ~ifelse(is_empty(xml_find_first(.x, p_doi)), 
  xml_find_first(e_doi),
  xml_find_first(p_doi))) %>% 
  length()

{if(is_empty(xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']"))
                          . else xml_find_all(".//Article/ELocationID[@EIdType='doi']")} %>% length()
# LOOP: take each article. IF "have both" take "IdType" only. Do for each node and append doi to resulting vector. Use for loop.

# Count of doi should be 372 BUT is 327 :) Correction needed.
xml_pubtype_n <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument") %>% xml_find_first(".//PublicationType") %>% length()
xml_nodes_count <- data.frame(xml_abstract_n, xml_pmid_n, xml_year_n, xml_author_n, xml_title_n, xml_doi_n, xml_pubtype_n)
print(xml_nodes_count)
rm(list = ls(pattern='_n$'))

### Split xml by items to data.frame rows ----
library(dplyr)
library(xml2)
library(purrr)
library(tidyr)
xml <- xml2::read_xml("input/example.xml")
rows <- xml %>% xml_find_all("//xmlsubsubnode")
rows_df <- data_frame(node = rows) %>%
  mutate(node_id = node %>% map(~ xml_find_first(., "ancestor::xmlnode")) %>% map(~ xml_attr(., "node-id"))) %>%
  mutate(subnode_id = node %>% map(~ xml_parent(.)) %>% map(~ xml_attr(., "subnode-id"))) %>%
  mutate(text = node %>% map(~ xml_text(.))) %>%
  select(-node)
# https://stackoverflow.com/questions/49253021/how-to-extract-xml-attr-and-xml-text-on-different-levels-with-xml2-and-purrr

xml_articles <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument")
xml_articles[[1]][["doc"]]
df_articles <- tibble(item = xml_articles)
ls_articles <- as.list(xml_articles)

### 5 Cases for DOI ----
xml_5_doi <- recs %>%
  xml_find_all(".//Article[@PubModel='Print']/../../PubmedData/ArticleIdList/ArticleID[@IdType='doi']") %>%
  length()

### THIS WORKS ----
xml_5_doi_tested <- recs %>%
  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>%
  xml_text()

xml_5_doi <- recs %>%
  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
                //Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
                //Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
                //Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle//ELocationID[@EIdType='doi']
               ") %>%
  length()

### CODE below generates 327 instead of 371 Captures ----
xml_5_doi <- recs %>%
  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
  //Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
  //Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
  //Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle//ELocationID[@EIdType='doi']
  ") %>%
  length()

# Analysis of problematic PubModel ----
recs %>% xml_find_all("//Article[@PubModel]='Electronic'") %>% length() # Correct, 371 because one is PubmedBookArticle

recs %>% xml_find_all("//PubmedArticle") %>% length() # Correct, 371 because one is PubmedBookArticle

recs %>% xml_find_all("//Article[@PubModel='Print']") %>% length() # 207
recs %>% xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() #165

recs %>% xml_find_all("//Article[@PubModel='Print-Electronic']") %>% length() # 138
recs %>% xml_find_all("//Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() # 137

recs %>% xml_find_all("//Article[@PubModel='Electronic']") %>% length() # 21
recs %>% xml_find_all("//Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() # 20

recs %>% xml_find_all("//Article[@PubModel='Electronic-eCollection']") %>% length() # 5
recs %>% xml_find_all("//Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() #5

PubmedArticle_n <- recs %>% xml_find_all("/PubmedArticleSet/PubmedArticle") %>% length() # Is correctly 371; PubmedArticle[369] missing; does not have ANY DOI
PubmedArticle_369 <- recs %>% xml_find_all("/PubmedArticleSet/PubmedArticle[369]//ArticleTitle") %>% xml_text()

models <- recs %>% xml_find_all("//Article[@PubModel]") %>% xml_attr("PubModel") %>% as.factor() %>% levels()
models

# Find which nodes are missing in 327 nodes. ----
node_path_n <- recs %>% xml_find_all("//*[@*='doi']") %>% length()
node_path <- recs %>% xml_find_all("//*[@*='doi']") %>% xml_path()
node_path
node_mode <- recs %>% xml_find_all("//*[@*='doi']/ancestor::Article[@PubModel]") %>% length()
write.csv(node_path, glue("{aa_path}node_path.csv"))

# xml_5_doi <- recs %>% 
#   xml_find_all(".//Article[@PubModel='Print']/ancestor::PubmedArticle") %>% xml_text()
#   xml_find_all(".//ArticleID[@IdType='doi']")
#   length()

xml_abstract <- recs %>% xml_find_all(".//Abstract") %>% xml_text()
xml_pmid <- recs %>% xml_find_all(".//MedlineCitation/PMID | .//BookDocument/PMID") %>% xml_text()
xml_year <- recs %>% xml_find_all(".//PubDate/Year | .//PubDate/MedlineDate") %>% xml_text()
xml_author <- recs %>% xml_find_all(".//AuthorList") %>% xml_find_first(".//Author/LastName") %>% xml_text()
xml_title <- recs %>% xml_find_all(".//ArticleTitle") %>% xml_text()
xml_doi <- recs %>% xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% xml_text()
xml_pubtype <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument") %>% xml_find_first(".//PublicationType") %>% xml_text()

pm_src <- data.frame(xml_title, 
                 xml_author,
                 xml_year,
                 xml_doi,
                 xml_pmid,
                 xml_abstract,
                 xml_pubtype)

pm <- pm_src %>% 
  mutate(FTlink = paste0("https://dx.doi.org/",pm_src$xml_doi)) %>% 
  mutate(CT = NA) %>% 
  mutate(PUI = NA) %>%
  mutate(PubDate = NA) %>%
  mutate(EBlink = NA) %>%
  mutate(OpenLink = NA) %>% 
  mutate(Info = NA) %>% 
  mutate(Src = "PubMed") %>% 
  select(xml_title, 
         xml_author, 
         xml_year, 
         FTlink, 
         Src, 
         Info, 
         PubDate, 
         xml_pubtype, 
         xml_abstract, 
         CT, 
         xml_pmid, 
         PUI, 
         xml_doi,
         EBlink,
         OpenLink)

names(pm) <- final_col_names
write_xlsx(pm, glue("{aa_path}pm_to_merge.xlsx"))
# rm(list = ls(pattern='^xml_'))
# rm(list=ls()[!ls() %in% c("eg")])

```
```{r}
#| label: Interating over PubMed (pm) article nodes
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
pm_query <- glue('peripheral edema measurement')
my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
# my_abstracts_txt <- fetch_pubmed_data(my_entrez_id, format = "abstract")
# print(my_abstracts_txt[1:45])
my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id)
print(paste0("Query retireved ",my_entrez_id$Count," records."))
# print(my_abstracts_xml)
# write(my_abstracts_xml, file = "PubMed_records_by_write.xml")
recs <- read_xml(my_abstracts_xml)

xml_arts <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument")
##  CONTINUE HERE ----
art_title <- xml_arts %>% map_dfc(pm_ex(.))
pm_ex <- function(x){ 
  art_title <- x %>% xml_find_first(".//ArticleTitle") %>% xml_text()
  return(art_title)
}
art_title <- xml_arts[[1]] %>% xml_find_first(".//ArticleTitle") %>% xml_text()
print(xml_arts[1])

```
```{r}
#| label: Split items children to tibble / data_frame
xml_in_df <- recs %>% xml_find_all(".//PubmedArticle | .//PubmedBookArticle" ) %>% 
  map(xml_children) %>% 
  map(~as_tibble(t(set_names(xml_text(.), xml_name(.))))) #or map_df
```

```{r}
#| label: Split items to tibble / data_frame
xml_in_df <- recs %>% xml_find_all(".//PubmedArticle | .//PubmedBookArticle" ) %>% 
  map(xml_contents) %>% 
  map(~as_tibble(t(set_names(xml_text(.), xml_name(.))))) #or map_df
```

```{r}
#| label: Merge results from embase (eb), Google Scholar (gs), and PubMed (pm)
eb <- read_xlsx(glue("{aa_path}eb_to_merge.xlsx"))
gs <- read_xlsx(glue("{aa_path}gs_to_merge.xlsx"))
pm <- read_xlsx(glue("{aa_path}pm_to_merge.xlsx"))

egp <- bind_rows(eb, gs, pm) %>% 
  arrange(desc(Year), Author, Src)
# rm(list=ls()[!ls() %in% c("eg")])
# write_xlsx(egp, glue("{aa_path}egp_v02.xlsx"))
```
# ToDo
- correct PubMed functionality
- gs extract surnames that include hyphen
- Introduce SrchIndex
- Add columns: Status, Priority

# ADDITIONAL INFO
### DOI by easyPubmed vignette

```{r}
#| label: PubMed connection
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
pm_query <- glue('peripheral edema measurement')
my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)

# Get articles XML
# my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id)
# print(paste0("Query retireved ",my_entrez_id$Count," records."))
# print(my_abstracts_xml)
# write(my_abstracts_xml, file = "PubMed_records_by_write.xml")

# recs <- read_xml(my_abstracts_xml) #  From DB connection
# recs <- read_xml(paste0(aa_path, "PubMed_records_by_write.xml")) # From file

ls_recs <- articles_to_list("PubMed_records_by_write.xml")

# Extract info form the list of articles
pm_df <- ls_recs %>% 
  map_df(~ article_to_df(.x, autofill = TRUE, getAuthors = TRUE, getKeywords = TRUE)) %>% 
  distinct(pmid, .keep_all=TRUE) %>%
  select(title, lastname, year, abstract, pmid, doi)
write_xlsx(pm_df, glue("{aa_path}pm_df_to_merge.xlsx"))

```
### DOI

you can get DOI using CrossRef API, implemented as
https://github.com/ropensci/rcrossref

Find out how many elements of **#gs_n a** are detected. Inspire yourself
in code **WebScrap_Austr_CZ_v12**

```{r}
#| label: Load Google Scholar page

```

```{python}
#| label: Check python installation
import os                   
print(os.environ['path'])  
```

## Retrieve articles from Google Scholar using SerpAPI

Log to the [SerpAPI site](https://serpapi.com/) Install the serpapi
package (package NOT in conda, pip=TRUE must be used):

```{r}
library(reticulate)
py_install("google-search-results", pip=TRUE )
```

Next load the SerpAPI interaction package.

```{python}
from serpapi import GoogleSearch
params = {
  "api_key": "c155eb329cff9b71b6b3cb8edbde7b049ad4cc6ec94a8a53b9a597915e18feb8",
  "engine": "google_scholar",
  "q": "S-lercanidipine",
  "hl": "en"
}
search = GoogleSearch(params)
results = search.get_dict()

```

## Shiny Documents

This Quarto document is made interactive using Shiny. Interactive
documents allow readers to modify parameters and see the results
immediately. Learn more about Shiny interactive documents at
<https://quarto.org/docs/interactive/shiny/>.

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are
automatically updated whenever inputs change. This demonstrates how a
standard R plot can be made interactive:

```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r}
#| context: server
output$distPlot <- renderPlot({
   x <- faithful[, 2]  # Old Faithful Geyser data
   bins <- seq(min(x), max(x), length.out = input$bins + 1)
   hist(x, breaks = bins, col = 'darkgray', border = 'white',
        xlab = 'Waiting time to next eruption (in mins)',
        main = 'Histogram of waiting times')
})
```

### 2022-11-02 Python_basic.qmd
Initial upload

---
title: "Python_basic"
format: html
---

# Code form "Basic Webscraper" by John Watson Rooney
[Source YouTube](https://www.youtube.com/watch?v=APukTnnwQEY&t=301s)

```{r}
library(reticulate)
py_install("bs4", method="conda" )
py_install("pandas", method="conda" )

```

```{python}
#| label: Scrape books from eshop

import requests
from bs4 import BeautifulSoup
import pandas as pd

book_list = []

for x in range (1, 3):
  print(x)
  url = f'http://books.toscrape.com/catalogue/page-{x}.html'
  r = requests.get(url)

  soup = BeautifulSoup(r.text, 'html.parser')

  article = soup.find_all('article', class_ = 'product_pod')

  for book in article:
    title = book.find_all('a')[1]['title']
    price = book.find('p', class_ = 'price_color').text[2:]
    instock = book.find('p', class_ = 'instock availability').text.strip()
    book = {
      'title': title,
      'price': price,
      'instock': instock
    }
    book_list.append(book)

print(len(book_list))
print(book_list[1:4])
df = pd.DataFrame(book_list)
print(df)

```

### 2022-11-02 web2pubmed.qmd
Initial upload

---
title: "web2pubmed"
author: "lizaharrison"
format: html
---
Code downloaded from 
[Github](https://github.com/lizaharrison/web2pubmed/blob/master/retrieval_cleansing_functions.py)

```{r}
#| label: Load R libraries
library(reticulate)
```

```{r}
#| label: Install Python packages
library(reticulate)
py_install(c("csv", 
             "eutils", 
             "requests",
             "lxml",
             "pandas",
             "itertools",
             "re",
             "time"), 
             method="conda" )

```
```{python}
#| label: Python code from GitHub

"""
Author: Eliza Harrison
This module contains the function used to retrieve PubMed article metadata from the PubMed
database using the NCBI E-Utilities API, as well as all functions used for the cleansing and
preparation of PubMed and webpage data.
"""

import csv
import eutils
import requests
import lxml
import pandas as pd
import itertools
import re
import time

# E-UTILITIES PUBMED RETRIEVAL FUNCTION
def eutils_from_df(input_df, chunksize, output_csv):
    """
    Retrieves and saves PubMed article content from PubMed via E-Utilities API to CSV file
    for set of PMIDs contained within Pandas Dataframe.
    Args:
        input_df: object name for Dataframe containing PMIDs of interest
        chunksize: number of PMIDs to pass to API
        output_csv: filename for CSV file to which article content will be saved
    Returns:
        CSV file with rows pertaining to article content for each PMID in input_csv.
        Columns correspond to fields retrieved via efetch client:
            'PMID', 'Year', 'Title', 'Abstract', 'Authors', 'Journal', 'Volume', 'Issue',
            'Pages', 'DOI', 'PMC'
        List and dataframe containing all PubMed article data successfully retrieved from database
    """

    # Specifies names for output csv column headers
    fieldnames = ['PMID',
                  'Year',
                  'Title',
                  'Abstract',
                  'Authors',
                  'Journal',
                  'Volume',
                  'Issue',
                  'Pages',
                  'DOI',
                  'PMC',
                  ]

    # Creates generator object containing each row in the input dataframe
    pm_chunks_gen = (input_df[i:i + chunksize] for i in range(0, len(input_df), chunksize))

    # Initialises empty list for compilation of article dictionaries into single container
    pm_article_list = []

    # Initialise eutils client to access NCBI E-Utilities API
    ec = eutils.Client()

    # Open CSV file to which each PubMed IDs downloaded data appended as a new row with specified column names
    with open(output_csv, 'a') as datafile:
        writer = csv.DictWriter(datafile,
                                fieldnames=fieldnames,
                                )
        writer.writeheader()

        # Converts each chunk of PubMed IDs from dataframe to list
        for chunk_count, chunk in zip(range(0, len(input_df)), pm_chunks_gen):
            try:
                index_list = list(chunk.index.values)
                chunk_list = list(chunk['PMID'])
                print('Chunk No. ' + str(chunk_count))

                # Passes chunk of PubMed IDs to E-Utilities API
                # Returns iterator object containing key data for each PubMed ID
                pm_article_set = iter(ec.efetch(db='pubmed',
                                                id=chunk_list,
                                                )
                                      )

                # Assigns each PubMed ID an index value
                # Iterates over pm_article_set to access data for each individual PubMed ID
                for id_index, id_value in enumerate(chunk_list):
                    print(index_list[id_index], id_value)
                    try:
                        # For each PMID index/value pair, iterates through article set
                        # Aggregates key article attributes for each PubMed ID into dictionary
                        pm_article = next(pm_article_set)
                        pm_article_content = dict(
                            PMID=str(pm_article.pmid),
                            Year=str(pm_article.year),
                            Title=str(pm_article.title),
                            Abstract=str(pm_article.abstract),
                            Authors=str(pm_article.authors),
                            Journal=str(pm_article.jrnl),
                            Volume=str(pm_article.volume),
                            Issue=str(pm_article.issue),
                            Pages=str(pm_article.pages),
                            DOI=str(pm_article.doi),
                            PMC=str(pm_article.pmc),
                            )

                        print(pm_article_content)
                        print(pm_article.pmid + ' - Download from Enterez complete')

                        # Saves dictionary as new item in list for later construction of dataframe
                        pm_article_list.append(pm_article_content)
                        print(pm_article.pmid + ' - Save to list complete')

                        # Writes dictionary to new row of csv file for future reference
                        writer.writerow(pm_article_content)
                        print(pm_article.pmid + ' - Write Data to CSV Complete')

                    # Except statements for content errors
                    except (StopIteration,
                            TypeError,
                            NameError,
                            ValueError,
                            lxml.etree.XMLSyntaxError,
                            eutils.exceptions.EutilsNCBIError,
                            ) as e1:
                        print('Error: ' + str(e1))
                        continue
                    # Except statements for network/connection errors
                    except(TimeoutError,
                           RuntimeError,
                           ConnectionError,
                           ConnectionResetError,
                           eutils.exceptions.EutilsRequestError,
                           requests.exceptions.ConnectionError,
                           ) as e2:
                        print('Error: ' + str(e2))
                        time.sleep(10)
                        continue

            except StopIteration:
                print('All downloads complete')
                break

    # Save list of dictionaries to dataframe & write to CSV file
    pm_article_df = pd.DataFrame.from_records(pm_article_list,
                                              columns=fieldnames,
                                              )
    print('Save to DataFrame complete')
    datafile.close()
    return pm_article_df

# LONGEST COMMON SUBSTRING ANALYSIS FUNCTIONS
def lcs_algorithm(str1, str2):
    """
    Extracts the longest common substring (words) between two strings.
    Args:
        str1: Input string 1
        str2: Input string 2
    Returns:
        lcs_set: The longest common substring shared between the two input strings.
   SOURCE: Code adapted from
        https://www.bogotobogo.com/python/python_longest_common_substring_lcs_algorithm_generalized_suffix_tree.php
    NOTE: Commented out sections correspond to code that allows for saving of more than one
        longest common substring (where len(lcs) is the same).
    """
    # str1_words = ''.join(str1.split())
    # str2_words = ''.join(str2.split())

    # Removes punctuation from string to prevent premature termination of longest common substring
    str1 = re.sub(r'[^\w\s]', '', str1)
    str2 = re.sub(r'[^\w\s]', '', str2)

    # Splits string into tuple of words, to compute lcs by word (vs character)
    str1_words = tuple(word for word in str1.lower().split())
    str2_words = tuple(word for word in str2.lower().split())

    m = len(str1_words)
    n = len(str2_words)

    matrix = [[0] * (n + 1) for i in range(m + 1)]

    longest = 0
    lcs_set = set()

    for i in range(m):

        for j in range(n):

            if str1_words[i] == str2_words[j]:
                x = matrix[i][j] + 1
                matrix[i+1][j+1] = x

                if x > longest:
                    longest = x
                    lcs_set = set()
                    lcs_set.add(str1_words[i - x + 1: i + 1])

                else:
                    pass

    lcs = [' '.join(tup) for tup in lcs_set]

    return lcs

def lcs_analysis(series, min_similarity):
    """
    Calculates and extracts longest common substring (lcs) between pairs of strings.
    Args:
        series:
        min_similarity:
    Returns:
        lcs_df:
    NOTE: Commented out sections correspond to code that allows for saving of more than one
        longest common substring (where len(lcs) is the same).
    """
    t0 = time.time()
    print('Beginning Longest Common Substring analysis...')

    # Removes all whitespace from series values to reduce size
    # series = series.apply(lambda x: ''.join(x.split()))  # This is stopping it from working on the title dataset

    # Generates all distinct pairs of series values
    article_pairs = itertools.combinations(series.index, 2)

    # Initialises empty list in which indices, lcs and %age match can be stored
    lcs_list = [[], [], [], []]

    for pair in article_pairs:
        index_1, index_2 = pair

        if index_1 != index_2:
            str1 = series[index_1]
            str2 = series[index_2]
            lcs = lcs_algorithm(str1, str2)

            if len(lcs) > 0:
                pct = (len(lcs[0]) / max(len(str1), len(str2))) * 100
                # pct = len(lcs[0]) / max(len(str1), len(str2)) * 100

                if pct > min_similarity:
                    print('%s - %s Longest common substring > min threshold' % (index_1, index_2))
                    lcs_list[0].append(index_1)
                    lcs_list[1].append(index_2)
                    lcs_list[2].append(lcs)
                    lcs_list[3].append(pct)

                else:
                    pass
            else:
                pass
        else:
            pass

    print('Longest common substring analysis of all records complete')
    lcs_df = pd.DataFrame(lcs_list).transpose()
    lcs_df.columns = ['article id 1', 'article id 2', 'lcs', '%age common']

    t1 = time.time()
    elapsed = round(t1 - t0, 2)
    print('%s seconds / %s minutes elapsed/n' % (elapsed, elapsed / 60))

    return lcs_df

# SELECTION OF 1:1 PMID-URL LINKS
def select_web_records(for_selection, full_corpus):
    subset = for_selection.loc[(~for_selection['pmid'].isin(full_corpus['pmid'].values))
                               & (~for_selection['url'].isin(full_corpus['url'].values))]

    selected_web_ids = []
    selected_urls = []

    for pmid in subset.loc[:, 'pmid'].unique():
        web_ids = subset.loc[subset['pmid'] == pmid].index.values
        urls = subset.loc[subset['pmid'] == pmid, 'url'].values
        corpus_text = subset.loc[subset['pmid'] == pmid, 'corpus_text'].values
        text_lengths = [len(text) for text in corpus_text]
        not_in_corpus = True

        while not_in_corpus is True:
            if len(web_ids) > 1:
                i = text_lengths.index(max(text_lengths))  # for selecting longest web article
                # i = random.randint(0, len(web_ids) - 1)  # for selecting random url
            elif len(web_ids) == 1:
                i = 0
            else:
                not_in_corpus = False
                break

            selected_id = web_ids[i]
            selected_url = urls[i]
            selected_corpus_text = corpus_text[i]

            if selected_url in selected_urls or \
                    selected_url in full_corpus['url'].values:
                web_ids = [x for x in web_ids if x != selected_id]
                urls = [x for x in urls if x != selected_url]
                corpus_text = [x for x in corpus_text if x != selected_corpus_text]
                text_lengths = [len(text) for text in corpus_text]
                not_in_corpus = True

            else:
                selected_web_ids.append(selected_id)
                selected_urls.append(selected_url)
                not_in_corpus = False
                print('Web record %s added to final corpus (%s)' % (selected_id, selected_url))

    full_corpus_updated = full_corpus.append(subset.loc[selected_web_ids])

    return full_corpus_updated
```

### 2022-11-02 ArticleAggregator_v05_pure.qmd
Streamlining the script and moving to Github

@@
 term <- "'peripheral edema' measurement"
-aa_path <- r"(C:\Users\I0172484\Documents\01 - Projects\LevoAmlo 2022 Cecko\Edema Study Oct2022\Method Literature Review\)"
-setwd(aa_path)
+aa_path <- r"(C:\Users\I0172484\Documents\03 - Scripts\R\WebScrap\ArticleAggregator_data\)"
+# setwd(aa_path)
 ```
@@
 #| label: Load file exported from EMBASE with standard columns
-eb_std_col <- read_xlsx(glue("{aa_path}Edema_Methods_eb_exp.xlsx"))
+eb_std_col <- read_xlsx(glue("{aa_path}eb_src.xlsx"))
 eb_std_col_names <- c("Title", "AuthorAll", "Year", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "FTlink", "EBlink", "OpenLink")
@@
   mutate(Src="EMBASE") %>%
+  mutate(SrcIndex=row_number()) %>% 
   select(Title, Author, Year, FTlink, Src, Info, everything())
 
-# write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
+write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
 # Correct for Van Der Lee manually

### 2022-11-02 ArticleAggregator_v05_pure.qmd
1st time FUNCTIONAL :)

@@
 
-write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
+# write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
 # Correct for Van Der Lee manually
@@
 # output_df <- data.frame(title=art_title, info=art_info, ref=art_ref)
-# write_xlsx(res_df, glue("{aa_path}gs_raw.xlsx"))
+# write_xlsx(res_df, glue("{aa_path}gs_src.xlsx"))
 ```
@@
   mutate(Src = "GoogleScholar") %>% 
+  mutate(SrcIndex=row_number()) %>%
   select(Title, Author, Year, FTlink, Src, Info, everything())
 
-write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))
+# write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))
+
 ## Manually input missing values ;)
@@
 ## Pubmed
+```{r}
+#| label: PubMed connection and article extraction
+api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
+pm_query <- "peripheral[tiab] edema[tiab] measurement[tiab]"
+# pm_query <- glue("{term}[tiab]")
+my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
+my_entrez_id$QueryTranslation
+my_entrez_id$Count
 
-You can get full-text link using Elink method of NIH e-utilities tool
+# Get articles XML
+my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id, 
+                                      retmax=500, 
+                                      format="xml", 
+                                      encoding="UTF-8")
+# print(paste0("Query retireved ",my_entrez_id$Count," records."))
+# print(my_abstracts_xml)
+write(my_abstracts_xml, file = "PubMed_records_by_write.xml")
 
-```{r}
-#| label: PubMed connection
-api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
-pm_query <- glue('peripheral edema measurement')
-my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
-# my_abstracts_txt <- fetch_pubmed_data(my_entrez_id, format = "abstract")
-# print(my_abstracts_txt[1:45])
+# recs <- read_xml(my_abstracts_xml) #  From DB connection
+# recs <- read_xml(paste0(aa_path, "PubMed_records_by_write.xml")) # From file
 
-my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id)
-print(paste0("Query retireved ",my_entrez_id$Count," records."))
-# print(my_abstracts_xml)
-# write(my_abstracts_xml, file = "PubMed_records_by_write.xml")
-# recs <- read_xml(my_abstracts_xml) #  From DB connection
-recs <- read_xml(paste0(aa_path, "PubMed_records_by_write.xml")) # From file
+ls_recs <- articles_to_list("PubMed_records_by_write.xml")
+# ls_recs <- my_abstracts_xml
 
-# USE THIS  TO EXTRACT ALL FIELDS AND CHARACTER VECTOR AND JOIN TO DATAFRAME
+# Extract info form the list of articles
+pm_df <- ls_recs %>% 
+  map_df(~ article_to_df(.x, autofill = TRUE, getAuthors = TRUE, getKeywords = TRUE)) %>% 
+  distinct(pmid, .keep_all=TRUE) %>%
+  select(title, lastname, year, abstract, pmid, doi)
 
-xml_abstract_n <- recs %>% xml_find_all(".//Abstract") %>% length()
-xml_pmid_n <- recs %>% xml_find_all(".//MedlineCitation/PMID | .//BookDocument/PMID") %>% length()
-xml_year_n <- recs %>% xml_find_all(".//PubDate/Year | .//PubDate/MedlineDate") %>% length()
-xml_author_n <- recs %>% xml_find_all(".//AuthorList") %>% xml_find_first(".//Author/LastName") %>% length()
-xml_title_n <- recs %>% xml_find_all(".//ArticleTitle") %>% length()
-
-# CONTINUE HERE ----
-# Some articles have Either EIdType OR IdType OR BOTH.I need IF to remove those with both
-xml_doi_n <- recs %>% xml_find_all(".//Article/ELocationID[@EIdType='doi']") %>% length() # N201
-xml_doi_n <- recs %>% xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi'] | .//Article/ELocationID[@EIdType='doi']") %>% length() # N528
-# WRONG if
-# inspire here: https://stackoverflow.com/questions/30604107/r-conditional-evaluation-when-using-the-pipe-operator
-xml_doi_n <- recs %>% {if(xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']") . else xml_find_all(".//Article/ELocationID[@EIdType='doi']")} %>% length()
-
-art <- ".//PubmedArticle | .//PubmedBookArticle"
-e_doi <- ".//Article/ELocationID[@EIdType='doi']"
-p_doi <- ".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']"
-n_art <- recs %>% xml_find_all(art)
-xml_doi_n <- recs %>% xml_find_all(art) %>%
-  map(if(is_empty(xml_find_first(p_doi)))
-  xml_find_first(e_doi) else
-  xml_find_first(p_doi)) %>% 
-  length()
-
-xml_doi_n <- recs %>% xml_find_all(art) %>%
-  map(., ~ifelse(is_empty(xml_find_first(.x, p_doi)), 
-  xml_find_first(e_doi),
-  xml_find_first(p_doi))) %>% 
-  length()
-
-{if(is_empty(xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']"))
-                          . else xml_find_all(".//Article/ELocationID[@EIdType='doi']")} %>% length()
-# LOOP: take each article. IF "have both" take "IdType" only. Do for each node and append doi to resulting vector. Use for loop.
-
-# Count of doi should be 372 BUT is 327 :) Correction needed.
-xml_pubtype_n <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument") %>% xml_find_first(".//PublicationType") %>% length()
-xml_nodes_count <- data.frame(xml_abstract_n, xml_pmid_n, xml_year_n, xml_author_n, xml_title_n, xml_doi_n, xml_pubtype_n)
-print(xml_nodes_count)
-rm(list = ls(pattern='_n$'))
-
-### Split xml by items to data.frame rows ----
-library(dplyr)
-library(xml2)
-library(purrr)
-library(tidyr)
-xml <- xml2::read_xml("input/example.xml")
-rows <- xml %>% xml_find_all("//xmlsubsubnode")
-rows_df <- data_frame(node = rows) %>%
-  mutate(node_id = node %>% map(~ xml_find_first(., "ancestor::xmlnode")) %>% map(~ xml_attr(., "node-id"))) %>%
-  mutate(subnode_id = node %>% map(~ xml_parent(.)) %>% map(~ xml_attr(., "subnode-id"))) %>%
-  mutate(text = node %>% map(~ xml_text(.))) %>%
-  select(-node)
-# https://stackoverflow.com/questions/49253021/how-to-extract-xml-attr-and-xml-text-on-different-levels-with-xml2-and-purrr
-
-xml_articles <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument")
-xml_articles[[1]][["doc"]]
-df_articles <- tibble(item = xml_articles)
-ls_articles <- as.list(xml_articles)
-
-### 5 Cases for DOI ----
-xml_5_doi <- recs %>%
-  xml_find_all(".//Article[@PubModel='Print']/../../PubmedData/ArticleIdList/ArticleID[@IdType='doi']") %>%
-  length()
-
-### THIS WORKS ----
-xml_5_doi_tested <- recs %>%
-  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>%
-  xml_text()
-
-xml_5_doi <- recs %>%
-  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
-                //Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
-                //Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
-                //Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle//ELocationID[@EIdType='doi']
-               ") %>%
-  length()
-
-### CODE below generates 327 instead of 371 Captures ----
-xml_5_doi <- recs %>%
-  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
-  //Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
-  //Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
-  //Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle//ELocationID[@EIdType='doi']
-  ") %>%
-  length()
-
-# Analysis of problematic PubModel ----
-recs %>% xml_find_all("//Article[@PubModel]='Electronic'") %>% length() # Correct, 371 because one is PubmedBookArticle
-
-recs %>% xml_find_all("//PubmedArticle") %>% length() # Correct, 371 because one is PubmedBookArticle
-
-recs %>% xml_find_all("//Article[@PubModel='Print']") %>% length() # 207
-recs %>% xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() #165
-
-recs %>% xml_find_all("//Article[@PubModel='Print-Electronic']") %>% length() # 138
-recs %>% xml_find_all("//Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() # 137
-
-recs %>% xml_find_all("//Article[@PubModel='Electronic']") %>% length() # 21
-recs %>% xml_find_all("//Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() # 20
-
-recs %>% xml_find_all("//Article[@PubModel='Electronic-eCollection']") %>% length() # 5
-recs %>% xml_find_all("//Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() #5
-
-PubmedArticle_n <- recs %>% xml_find_all("/PubmedArticleSet/PubmedArticle") %>% length() # Is correctly 371; PubmedArticle[369] missing; does not have ANY DOI
-PubmedArticle_369 <- recs %>% xml_find_all("/PubmedArticleSet/PubmedArticle[369]//ArticleTitle") %>% xml_text()
-
-models <- recs %>% xml_find_all("//Article[@PubModel]") %>% xml_attr("PubModel") %>% as.factor() %>% levels()
-models
-
-# Find which nodes are missing in 327 nodes. ----
-node_path_n <- recs %>% xml_find_all("//*[@*='doi']") %>% length()
-node_path <- recs %>% xml_find_all("//*[@*='doi']") %>% xml_path()
-node_path
-node_mode <- recs %>% xml_find_all("//*[@*='doi']/ancestor::Article[@PubModel]") %>% length()
-write.csv(node_path, glue("{aa_path}node_path.csv"))
-
-# xml_5_doi <- recs %>% 
-#   xml_find_all(".//Article[@PubModel='Print']/ancestor::PubmedArticle") %>% xml_text()
-#   xml_find_all(".//ArticleID[@IdType='doi']")
-#   length()
-
-xml_abstract <- recs %>% xml_find_all(".//Abstract") %>% xml_text()
-xml_pmid <- recs %>% xml_find_all(".//MedlineCitation/PMID | .//BookDocument/PMID") %>% xml_text()
-xml_year <- recs %>% xml_find_all(".//PubDate/Year | .//PubDate/MedlineDate") %>% xml_text()
-xml_author <- recs %>% xml_find_all(".//AuthorList") %>% xml_find_first(".//Author/LastName") %>% xml_text()
-xml_title <- recs %>% xml_find_all(".//ArticleTitle") %>% xml_text()
-xml_doi <- recs %>% xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% xml_text()
-xml_pubtype <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument") %>% xml_find_first(".//PublicationType") %>% xml_text()
-
-pm_src <- data.frame(xml_title, 
-                 xml_author,
-                 xml_year,
-                 xml_doi,
-                 xml_pmid,
-                 xml_abstract,
-                 xml_pubtype)
-
-pm <- pm_src %>% 
-  mutate(FTlink = paste0("https://dx.doi.org/",pm_src$xml_doi)) %>% 
+# Add columns
+names(pm_df) <- c("Title", "Author", "Year", "Abstract", "PMID", "DOI")
+pm <- pm_df %>% 
+  mutate(Info = NA) %>% 
+  mutate(PubDate = NA) %>% 
+  mutate(PubType = NA) %>%
   mutate(CT = NA) %>%
   mutate(PUI = NA) %>%
-  mutate(PubDate = NA) %>%
   mutate(EBlink = NA) %>%
   mutate(OpenLink = NA) %>%
-  mutate(Info = NA) %>% 
+  mutate(FTlink = paste0("https://dx.doi.org/",pm_df$DOI)) %>% 
   mutate(Src = "PubMed") %>% 
-  select(xml_title, 
-         xml_author, 
-         xml_year, 
-         FTlink, 
-         Src, 
-         Info, 
-         PubDate, 
-         xml_pubtype, 
-         xml_abstract, 
-         CT, 
-         xml_pmid, 
-         PUI, 
-         xml_doi,
-         EBlink,
-         OpenLink)
-
-names(pm) <- final_col_names
+  mutate(SrcIndex=row_number()) %>%
+  select(Title, Author, Year, FTlink, Src, Info, everything())
 write_xlsx(pm, glue("{aa_path}pm_to_merge.xlsx"))
-# rm(list = ls(pattern='^xml_'))
-# rm(list=ls()[!ls() %in% c("eg")])
 
 ```
-```{r}
-#| label: Interating over PubMed (pm) article nodes
-api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
-pm_query <- glue('peripheral edema measurement')
-my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
-# my_abstracts_txt <- fetch_pubmed_data(my_entrez_id, format = "abstract")
-# print(my_abstracts_txt[1:45])
-my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id)
-print(paste0("Query retireved ",my_entrez_id$Count," records."))
-# print(my_abstracts_xml)
-# write(my_abstracts_xml, file = "PubMed_records_by_write.xml")
-recs <- read_xml(my_abstracts_xml)
-
-xml_arts <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument")
-##  CONTINUE HERE ----
-art_title <- xml_arts %>% map_dfc(pm_ex(.))
-pm_ex <- function(x){ 
-  art_title <- x %>% xml_find_first(".//ArticleTitle") %>% xml_text()
-  return(art_title)
-}
-art_title <- xml_arts[[1]] %>% xml_find_first(".//ArticleTitle") %>% xml_text()
-print(xml_arts[1])
-
-```
-```{r}
-#| label: Split items children to tibble / data_frame
-xml_in_df <- recs %>% xml_find_all(".//PubmedArticle | .//PubmedBookArticle" ) %>% 
-  map(xml_children) %>% 
-  map(~as_tibble(t(set_names(xml_text(.), xml_name(.))))) #or map_df
-```
-
-```{r}
-#| label: Split items to tibble / data_frame
-xml_in_df <- recs %>% xml_find_all(".//PubmedArticle | .//PubmedBookArticle" ) %>% 
-  map(xml_contents) %>% 
-  map(~as_tibble(t(set_names(xml_text(.), xml_name(.))))) #or map_df
-```
-
+## Merge the results
 ```{r}
@@
 egp <- bind_rows(eb, gs, pm) %>%
-  arrange(desc(Year), Author, Src)
+  mutate(Status=NA) %>% 
+  mutate(Priority=NA) %>% 
+  arrange(desc(Year), Author, Src) %>% 
+  select(Status, Priority, everything())
 # rm(list=ls()[!ls() %in% c("eg")])
-# write_xlsx(egp, glue("{aa_path}egp_v02.xlsx"))
+write_xlsx(egp, glue("{aa_path}egp_v01.xlsx"))
 ```
+
 # ToDo
-- correct PubMed functionality
 - gs extract surnames that include hyphen
-- Introduce SrchIndex
 - Add columns: Status, Priority

### 2022-11-03 Python_basic.qmd
The First steps with Selenium.

@@
 py_install("pandas", method="conda" )
+py_install("selenium", method="conda" )
 
@@
 ```
+
+```{python}
+#| label: Selenium installation with Chrome Webdriver
+
+# Source: https://www.youtube.com/watch?v=pUUhvJvs-R4
+
+from selenium import webdriver
+from selenium.webdriver.common.keys import Keys
+
+drv_path = "C:\\Users\\I0172484\\Documents\WebDriver\\chromedriver.exe"
+driver = webdriver.Chrome(drv_path)
+
+url="http://the-internet.herokuapp.com/login"
+driver.get(url)
+
+driver.find_element("xpath", '//*[@id="username"]').send_keys('tomsmith')
+driver.find_element("xpath", '//*[@id="password"]').send_keys('SuperSecretPassword!')
+driver.find_element("xpath", '//*[@id="login"]/button').click()
+
+```

### 2022-11-03 Python_basic.qmd
Selenium Login and implicit wait

@@
 from selenium.webdriver.common.keys import Keys
+from selenium.webdriver.support.ui import WebDriverWait
 
@@
 driver.find_element("xpath", '//*[@id="login"]/button').click()
+# driver.quit()
+
+# Wait for response part
+url02="https://the-internet.herokuapp.com/dynamic_loading/2"
+driver.get(url02)
+driver.find_element("xpath", '//*[@id="start"]/button').click()
+driver.implicitly_wait(10)
+text = driver.find_element("xpath", '//*[@id="finish"]/h4').text
+print(text)
 

### 2022-11-08 ArticleAggregator_v05_pure.qmd
Article Aggreagor PubMed Term added

@@
 final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT",      "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
-term <- "'peripheral edema' measurement"
+term <- "peripheral edema measurement"
 aa_path <- r"(C:\Users\I0172484\Documents\03 - Scripts\R\WebScrap\ArticleAggregator_data\)"
@@
 gs_term <- str_replace_all(term, " ", "+")
-my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=0%2C5&q={gs_term}")
+# my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=0%2C5&q={gs_term}")
+
+# For Title; including patents; excluding citation
+my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=2007&as_vis=1&q=allintitle%3A+{gs_term}&btnG=")
+
 gs <- read_html(my_uri)
@@
 api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
-pm_query <- "peripheral[tiab] edema[tiab] measurement[tiab]"
+
+sl_term <- str_split(term, " ", simplify=TRUE)
+pm_query <- str_c(sl_term,"[tiab] ", collapse="")
+
+# pm_query <- "peripheral[tiab] edema[tiab] measurement[tiab]"
 # pm_query <- glue("{term}[tiab]")
+
 my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)

### 2022-11-08 pandas-master/Pandas.qmd
Article Aggreagor PubMed Term added

---
title: "Pandas"
format: html
---

# Code form "Basic Webscraper" by John Watson Rooney
[Source YouTube](https://www.youtube.com/watch?v=vmEHCJofslg)

```{r}
library(reticulate)
py_install("pandas", method="conda" )
py_install("openpyxl", method="conda" )
```

```{python}
#| label: Scrape books from eshop

import pandas as pd
import os

os.getcwd()
df = pd.read_csv("pokemon_data.csv")
# df_x = pd.read_excel("pokemon_data.xlsx")
# df_txt = pd.read_csv("pokemon_data.txt", delimiter='\t')
print(df.head(3))
print(df.tail(3))
print(df.columns)
print(df[['Name', 'Type 1', 'HP']][0:5])

 ```

### 2022-11-08 ArticleAggregator_v05_pure.qmd
ToDo updated
ToDo update

@@
 - gs extract surnames that include hyphen
-- Add columns: Status, Priority
+- gs with single page outcome
+- save final table with search_term name (instead of egp)
+- delete variables after writing to xlsx_to_merge
+- delete temporary files (to_marge, PubMed.xml etc.)
 

### 2022-11-23 ArticleAggregator.qmd
Live version only

--- 2022-11-08 ArticleAggregator_v05_pure.qmd
@@
 ---
-title: "Peripheral Edema measurement methods (by ArticleAggregator_v03)"
-author: "ReCodeR"
+title: "Peripheral Edema measurement methods (by ArticleAggregator_v05)"
+author: "ReCodeRa"
 format: html

### 2023-02-17 ArticleAggregatorCS.qmd
Before import of eb_to_merge.xlsx to CodeSpace

--- 2022-11-08 ArticleAggregator_v05_pure.qmd
@@
 ---
-title: "Peripheral Edema measurement methods (by ArticleAggregator_v03)"
-author: "ReCodeR"
+title: "continuous tadalafil (by ArticleAggregator_v05)"
+author: "ReCodeRa"
 format: html
@@
 install.packages("httr")
+install.packages("readxl")
 install.packages("writexl")
@@
 final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
-term <- "peripheral edema measurement"
-aa_path <- r"(C:\Users\I0172484\Documents\03 - Scripts\R\WebScrap\ArticleAggregator_data\)"
-# setwd(aa_path)
+term <- "continuous tadalafil"
+aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/"
+setwd(aa_path)
 ```

### 2023-02-21 ArticleAggregatorCS.qmd
Results for tadalafil continous ready in egp.xlsx
ramipril cough amlodipine

@@
 ---
-title: "continuous tadalafil (by ArticleAggregator_v05)"
+title: "ramipril cough amlodipine (by ArticleAggregator_v05)"
 author: "ReCodeRa"
@@
 -   Scholar (including patents)
+
+## Procedure
+- EMBASE search: search in ""
 
@@
 final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
-term <- "continuous tadalafil"
-aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/"
+term <- "ramipril cough amlodipine"
+aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/rami/"
 setwd(aa_path)
@@
 
-# write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
+write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
 # Correct for Van Der Lee manually
@@
 
-# write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))
+write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))
 

### 2023-02-21 ArticleAggregatorCS.qmd
ramipril cough amlodipoine seach finished

@@
 ## Procedure
-- EMBASE search: search in ""
+- EMBASE search: Zentiva Network or VPN, search in "Title, Abstract or Author Keywords"
+- Export result in Excel Column Format with following fields: 
+    1. Title
+    2. Author names
+    3. Publication Year
+    4. Publication type
+    5. Date of publication
+    6. Digital Object Identifier (DOI)
+    7. Medline PMID
+    8. Embase identification number (PUI)
+    9. Abstract
+    10. Clinical Trial Number
+    11. Full text link
+    12. Embase link
+    13. Open URL Link
+- Save to working directory as "eb_src.xlsx"
+- Install packages
+- Load packages
+- Set environment check "term" and "aa_path"
+- Decide if use Scholar only for in titles search or full search (enable corresponding url)
+-
 
@@
 gs_term <- str_replace_all(term, " ", "+")
-# my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=0%2C5&q={gs_term}")
+my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=0%2C5&q={gs_term}")
 
 # For Title; including patents; excluding citation
-my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=2007&as_vis=1&q=allintitle%3A+{gs_term}&btnG=")
+# my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=2007&as_vis=1&q=allintitle%3A+{gs_term}&btnG=")
 

### 2023-02-21 ArticleAggregatorCS.qmd
Final egp_v01.xlsx downloaded

@@
 - Decide if use Scholar only for in titles search or full search (enable corresponding url)
--
+- Final Excel table as "egp_v01.xlsx"
 

### 2023-02-22 ArticleAggregatorCS.qmd
eb_src.xlsx uploaded to AAdata-Refr_ED

@@
 ---
-title: "ramipril cough amlodipine (by ArticleAggregator_v05)"
+title: "refractory erectile dysfunction (by ArticleAggregator_v05)"
 author: "ReCodeRa"
@@
 final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
-term <- "ramipril cough amlodipine"
-aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/rami/"
+term <- "refractory erectile dysfunction"
+aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/refrac_ED/"
 setwd(aa_path)

### 2023-02-22 ArticleAggregatorCS.qmd
PubMed missing

@@
 term <- "refractory erectile dysfunction"
-aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/refrac_ED/"
+aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/rami/refrac_ED/"
 setwd(aa_path)

### 2023-02-22 ArticleAggregatorCS.qmd
PubMed fail even with new APIkey

@@
 #| label: PubMed connection and article extraction
-api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
+# api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
+api_key <- "7677957ef60aa19aa6c5856e126b696d6408"
 

### 2023-02-22 ArticleAggregatorCS.qmd
PubMed search skipped

@@
 
+## Merge EB and GS ony
+```{r}
+#| label: Merge results from embase (eb), Google Scholar (gs), and PubMed (pm)
+eb <- read_xlsx(glue("{aa_path}eb_to_merge.xlsx"))
+gs <- read_xlsx(glue("{aa_path}gs_to_merge.xlsx"))
+# pm <- read_xlsx(glue("{aa_path}pm_to_merge.xlsx"))
+
+eg <- bind_rows(eb, gs) %>%
+  mutate(Status=NA) %>% 
+  mutate(Priority=NA) %>% 
+  arrange(desc(Year), Author, Src) %>% 
+  select(Status, Priority, everything())
+# rm(list=ls()[!ls() %in% c("eg")])
+write_xlsx(eg, glue("{aa_path}eg_v02.xlsx"))
+```
+
 # ADDITIONAL INFO
